Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England: Supplementary materials

### 2022-03-30 manuscript/draft-supplement-v1-1.Rmd
some revisions

    modell <- model
    riskdiff_ns %>%
      filter(model==modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=0), colour='black')+
      geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
      geom_rect(aes(xmin=tstop, xmax=lead_tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_continuous(
        expand = expansion(0),
        sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(-3, 3))+
      scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
      scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
      labs(
        x=NULL,
        y="Difference\nin cumul. incidence\nper 1000",
        colour=NULL
      )+
      theme_minimal(base_size = 9)+
      theme(
        axis.line.y.left = element_line(colour = "black"),

@@

    hazard_ns %>% 
      filter(model == modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=1), colour='black')+
      geom_step(aes(x=tstop, y=hr), colour='orchid4', direction="vh")+
      geom_rect(aes(xmin=lag_tstop, xmax=tstop, ymin=hr.ll, ymax=hr.ul), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_log10(
        breaks=c(0.1, 0.2, 0.5, 1, 2, 5, 10),
        sec.axis = dup_axis(name="Lower hazard after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(0.1, 10))+
      labs(
        x = "Days since first dose",
        y = "Hazard ratio"
      )+
      theme_minimal(base_size = 9)+
      theme(
        axis.line.y.left = element_line(colour = "black"),

@@

  plot_riskdiff_pw <-
    riskdiff_pw %>%
    filter(model==3) %>%
    ggplot()+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    geom_rect(aes(xmin=tstop, xmax=lead_tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Higher incidence after \n <- ChAdOx1 / BNT162b2 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(-3, 3))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Difference\nin cumul. incidence\nper 1000",
      colour=NULL
    )+
    theme_minimal(base_size = 9)+
    theme(
      axis.line.y.left = element_line(colour = "black"),

@@

  ## hazard ratio
  plot_hazard_pw <-
    hazard_pw %>%
    filter(model==3) %>%
    ggplot()+
    geom_hline(aes(yintercept=1), colour='black')+
    geom_step(aes(x=tstop, y=hr), colour='orchid4', direction="vh")+
    geom_rect(aes(xmin=lag_tstop, xmax=tstop, ymin=hr.ll, ymax=hr.ul), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.1, 0.2, 0.5, 1, 2, 5, 10),
      sec.axis = dup_axis(name="Higher hazard after \n <- ChAdOx1 / BNT162b2 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(0.1, 10))+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio"
    )+
    theme_minimal(base_size = 9)+
    theme(
      axis.line.y.left = element_line(colour = "black"),

>>>>

    modell <- model
    riskdiff_ns %>%
      filter(model==modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=0), colour='black')+
      geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
      geom_rect(aes(xmin=tstop, xmax=lead_tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_continuous(
        expand = expansion(0),
        sec.axis = dup_axis(name="Higher incidence after \n <- ChAdOx1 | BNT162b2 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(-3, 3))+
      scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
      scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
      labs(
        x=NULL,
        y="Difference\nin cumul. incidence\nper 1000",
        colour=NULL
      )+
      theme_minimal(base_size = 9)+
      theme(
        axis.line.y.left = element_line(colour = "black"),

@@

    hazard_ns %>% 
      filter(model == modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=1), colour='black')+
      geom_step(aes(x=tstop, y=hr), colour='orchid4', direction="vh")+
      geom_rect(aes(xmin=lag_tstop, xmax=tstop, ymin=hr.ll, ymax=hr.ul), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_log10(
        breaks=c(0.1, 0.2, 0.5, 1, 2, 5, 10),
        sec.axis = dup_axis(name="Higher hazard after \n <- ChAdOx1 | BNT162b2 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(0.1, 10))+
      labs(
        x = "Days since first dose",
        y = "Hazard ratio"
      )+
      theme_minimal(base_size = 9)+
      theme(
        axis.line.y.left = element_line(colour = "black"),

@@

  plot_riskdiff_pw <-
    riskdiff_pw %>%
    filter(model==3) %>%
    ggplot()+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    geom_rect(aes(xmin=tstop, xmax=lead_tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Higher incidence after \n <- ChAdOx1 | BNT162b2 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(-3, 3))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Difference\nin cumul. incidence\nper 1000",
      colour=NULL
    )+
    theme_minimal(base_size = 9)+
    theme(
      axis.line.y.left = element_line(colour = "black"),

@@

  ## hazard ratio
  plot_hazard_pw <-
    hazard_pw %>%
    filter(model==3) %>%
    ggplot()+
    geom_hline(aes(yintercept=1), colour='black')+
    geom_step(aes(x=tstop, y=hr), colour='orchid4', direction="vh")+
    geom_rect(aes(xmin=lag_tstop, xmax=tstop, ymin=hr.ll, ymax=hr.ul), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_wrap(facets=vars(outcome_descr), nrow=1, scales="free_y")+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=28),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.1, 0.2, 0.5, 1, 2, 5, 10),
      sec.axis = dup_axis(name="Higher hazard after \n <- ChAdOx1 | BNT162b2 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(0.1, 10))+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio"
    )+
    theme_minimal(base_size = 9)+
    theme(
      axis.line.y.left = element_line(colour = "black"),
